Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-09-23 AO_bondedSi.tex
remove Figure 1 and discussion of temperature dependence

There are several good reviews of Si bonding that include accounts of the history of the field and a description of process alternatives, metrology, and problems \cite{1998AnRMS..28..215G,Masteika2014}.  The foundation paper on Si bonding came in 1986 \cite{1986JAP....60.2987S}. After that, there was a sequence of papers that used IR imaging to look for evidence of defects in the bond. Stengl et al. (1988) and G{\"o}esele et al. (1995) \cite{1988JaJAP..27L2364S, 1995ApPhL..67.3614G} directly monitored the bond propagation with time-lapse IR imaging. Lehman et al. 1989 and Goesele et al. \cite{1989JaJAP..28L2141L, 1995ApPhL..67.3614G} demonstrated gap-free bonding in a micro- cleanroom, in which the bonding process occurs immediately after a rinse-spin-vacuum cycle inside of a vacuum enclosure.  Other authors investigated the growth of bubbles at bond interfaces with time and the elimination of some or all of these bubbles after annealing bonded parts at temperatures of $800-1100\;^\circ$C \cite{Horn2009, Masteika2014}.

@@

Our measurement technique exploits the large Fresnel reflection \cite{2001opt4.book.....H} at the Si$-$vacuum interface.  The refractive index of silicon is one of the highest of any commonly used optical material.  Figure \ref{figSiIndexFinesse} shows the refractive index at room temperature \cite{2006SPIE.6273E..77F} that we assume through this article.  The Fresnel reflection is about $30\;\%$ per surface, much larger than the $4-7\;\%$ per surface of the many optical materials with refractive indices in the range $1.5-1.7$.

\begin{figure}[htbp]
\includegraphics[width=0.95\columnwidth]{figs/SiIndexAOmgsFinesseFig.pdf}
\caption{Plot of refractive index, $n$, and coefficient of finesse, $F$, as a function of wavelength, $\lambda$.\label{figSiIndexFinesse} We computed the temperature dependent refractive index from the tabulations of \cite{2006SPIE.6273E..77F}.  The coefficient of finesse is defined in Equation \ref{eq:FabPerot}.}
\end{figure}

We can treat a small Si$-$Si interface gap between two almost-bonded silicon parts as a low-Finesse Fabry-P\'{e}rot etalon\cite{2007fuph.book.....S}.  The key property of an etalon is that it has a cavity enclosed between two smooth and parallel reflective surfaces where the requirements for smoothness and parallelism depend on the reflective finesse of the cavity.  For the narrow air gaps we consider here and for the modest reflectivity of a Si-vacuum interface, most gaps at Si$-$Si bonds will form effective etalons over most of their area.  The transmission through a Fabry-P\'{e}rot depends on the wavelength of light, the reflectivity of the etalon sidewalls, and the size of the gap.  We compute the reflectivity for an Si$-$vacuum interface, which is a modest function of wavelength through the refractive index of Silicon, $n(\lambda, T)$ \cite{2006SPIE.6273E..77F}, as shown in Figure \ref{figSiIndexFinesse}.  We drop the subscripts on the refractive index $n(\lambda, T) \rightarrow n$ and the coefficient of finesse $F(\lambda, T) \rightarrow F$ for clarity.  The computation is simply Fresnel's law at normal incidence:

@@

\subsection{Spatially resolved measurements across the face of a sample}
We acquired spatially resolved measurements of the pair of bonded parts VG09-12, (Tables \ref{tbl_experiments} and \ref{tbl_meshPatterns}).  We translated the sample through the measurement beam and measured a transmission spectrum at 25 unique adjacent positions.  We chose a 2 mm step size, which is comparable to the beam width.  We sampled across the mesh pattern and into the off-mesh pattern (Figure \ref{figVG0912_STA_illus}).

>>>>

There are several good reviews of Si bonding that include accounts of the history of the field and a description of process alternatives, metrology, and problems \cite{1998AnRMS..28..215G,Masteika2014}.  The foundation paper on Si bonding came in 1986 \cite{1986JAP....60.2987S}. After that, there was a sequence of papers that used IR imaging to look for evidence of defects in the bond. Stengl et al. (1988) and G{\"o}esele et al. (1995) \cite{1988JaJAP..27L2364S, 1995ApPhL..67.3614G} directly monitored the bond propagation with time-lapse IR imaging. Lehman et al. 1989 and G{\"o}esele et al. \cite{1989JaJAP..28L2141L, 1995ApPhL..67.3614G} demonstrated gap-free bonding in a micro- cleanroom, in which the bonding process occurs immediately after a rinse-spin-vacuum cycle inside of a vacuum enclosure.  Other authors investigated the growth of bubbles at bond interfaces with time and the elimination of some or all of these bubbles after annealing bonded parts at temperatures of $800-1100\;^\circ$C \cite{Horn2009, Masteika2014}.

@@

Our measurement technique exploits the large Fresnel reflection \cite{2001opt4.book.....H} at the Si$-$vacuum interface.  The refractive index of silicon is one of the highest of any commonly used optical material, at about 3.5 at a wavelength $\lambda = 1.2 \;\mu$m at room temperature \cite{2006SPIE.6273E..77F}.  The Fresnel reflection is about $30\;\%$ per surface, much larger than the $4-7\;\%$ per surface of the many optical materials with refractive indices in the range $1.5-1.7$.

We can treat a small Si$-$Si interface gap between two almost-bonded silicon parts as a low-Finesse Fabry-P\'{e}rot etalon\cite{2007fuph.book.....S}.  The key property of an etalon is that it has a cavity enclosed between two smooth and parallel reflective surfaces where the requirements for smoothness and parallelism depend on the reflective finesse of the cavity.  For the narrow air gaps we consider here and for the modest reflectivity of a Si-vacuum interface, most gaps at Si$-$Si bonds will form effective etalons over most of their area.  The transmission through a Fabry-P\'{e}rot depends on the wavelength of light, the reflectivity of the etalon sidewalls, and the size of the gap.  We compute the Si$-$vacuum interface reflectivity, which is a modest function of wavelength, through the refractive index of Silicon, $n(\lambda, T)$ \cite{2006SPIE.6273E..77F}, where $T$ is temperature.  We adopt room temperature values through this article.  We drop the subscripts on the refractive index $n(\lambda, T) \rightarrow n$ and the coefficient of finesse $F(\lambda, T) \rightarrow F$ for clarity.  The computation is simply Fresnel's law at normal incidence:

@@

\subsection{Spatially resolved measurements across the face of a sample}
We acquired spatially resolved measurements of the pair of bonded parts VG09-12, (Tables \ref{tbl_experiments} and \ref{tbl_meshPatterns}).  We translated the sample through the measurement beam and measured a transmission spectrum at 25 unique adjacent positions.  We chose a 2 mm step size, which is comparable to the beam width.  We sampled across the mesh pattern and into the off-mesh pattern of sample VG09-12 (Figure \ref{figVG0912_STA_illus}).
